Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

\paragraph{Quantitative experiments.}
We benchmark DAU against DDPG on classic control benchmarks: Pendulum,
Cartpole, BipedalWalker, Ant, and Half-Cheetah environments from OpenAI
Gym. For Pendulum and Ant, DDPG is able to learn for the highest
$\deltat$ but fails for the others, while DAU remains reasonably
invariant to the time discretization. On BipedalWalker, DDPG is never
able to learn while DAU is achieving decent performance for all the
$\deltat$'s. On Cartpole and Half-Cheetah, the results are less clear. On
Cartpole, noise dominates, which makes interpretation difficult. On Half-Cheetah, DAU is not clearly more invariant to time discretization than
DDPG. This could be explained by the multiple suboptimal regimes that
coexist in the Half-Cheetah environment (walking on the head, walking on
the back). \TODO{Removed, was unclear: ``and that DAU may fail to correctly weight the performance of
each regime (as explained in Section \ref{sec:discussions}).''}

>>>>

\paragraph{Quantitative experiments.}
We benchmark DAU against DDPG on classic control benchmarks: Pendulum,
Cartpole, BipedalWalker, Ant, and Half-Cheetah environments from OpenAI
Gym. For Pendulum and Ant, DDPG is able to learn for the highest
$\deltat$ but fails for the others, while DAU remains reasonably
invariant to the time discretization. On BipedalWalker, DDPG is never
able to learn while DAU is achieving decent performance for all the
$\deltat$'s. On Cartpole and Half-Cheetah, the results are less clear. On
Cartpole, noise dominates, which makes interpretation difficult. On Half-Cheetah, DAU is not clearly more invariant to time discretization than
DDPG. This could be explained by the multiple suboptimal regimes that
coexist in the Half-Cheetah environment (walking on the head, walking on
the back). \TODO{Removed, was unclear: ``and that DAU may fail to correctly weight the performance of
each regime (as explained in Section \ref{sec:discussions}).'' Anyway
this regimes exist for all algorithms...}
